Dependent Object Types

### 2012-09-03 doc/candidacy/report.tex
a bit more intro

Path-dependent types are a key concept in the DOT calculus, and a
unifying concept of the three papers we choose to study. A {\it
  dependent type} is a type which depends on a term. A {\it
  path-dependent type} is a limited form of dependent type, in which a
type depends on a path: a chain of immutable fields or
variables. Path-dependent types arise when terms, usually objects, can
have types as members.

@@

\section{Survey of the Selected Papers}%: The Giants upon whose shoulders I will stand

@@

\section{Research Proposal} %: How I Plan to Revolutionize the World

>>>>

Path-dependent types are a key concept in the DOT calculus, and a
unifying concept of the three papers we choose to study. A {\it
  dependent type} is a type which depends on a term. A {\it
  path-dependent type} is a limited form of dependent type, in which a
type depends on a path: a chain of immutable fields or
variables. Path-dependent types arise when terms, usually objects, can
have types as members. Abstract type members, together with explicit
selftypes and modular mixin composition have been identified as key
abstractions for the construction of reusable components~\cite{SCA}.

\subsubsection*{Scala Example} In the code below,
\code{type T} is an abstract type member of \code{AbsCell}. In a
library method taking an abstract cell \code{c}, the expression
\code{c.set(c.init)} is well-typed because \code{c.init} has type
\code{c.T} and \code{c.set} has the type of a function that expects a
parameter of type \code{c.T}. Note that \code{c.T} is a path-dependent
type. \lstinputlisting{intro.scala}

@@

In section~\ref{survey}, we survey selected previous work related to
path-dependent types. Whenever possible, we contrast the formalisms
with concrete examples in Scala. In section~\ref{proposal}, we discuss
in more details our proposal for a new type-theoretic foundation of
Scala based on path-dependent types.

\section{Survey of the Selected Papers}\label{survey}%: The Giants upon whose shoulders I will stand

@@

\section{Research Proposal}\label{proposal}%: How I Plan to Revolutionize the World

### 2012-09-03 doc/candidacy/slides.tex
a bit more intro

\documentclass{beamer}
\usepackage{minted}
\usemintedstyle{eclipse}
\begin{document}

>>>>

\documentclass{beamer}

\usepackage{minted}
\usemintedstyle{eclipse}

\begin{document}

\begin{frame}
\frametitle{DOT: Dependent Object Types}

The DOT calculus proposes a new \emph{type-theoretic foundation} for Scala
and languages like it. It models
\begin{itemize}
\item \emph{path-dependent types}
\item abstract type members
\item mixture of nominal and structural typing via refinement types
\end{itemize}

It does not model
\begin{itemize}
\item inheritance and mixin composition
\item what's currently in Scala
\end{itemize}

\end{frame}

\begin{frame}[fragile]{Path-dependent types}

\begin{description}[path-dependent type]
\item[path-dependent type] limited form of \emph{dependent type}, in which a type depends on a \emph{path}
\item[dependent type] a type which depends on a term
\item[path] a chain of immutable fields or variables
\end{description}

\inputminted[frame=lines,fontsize=\footnotesize]{scala}{intro.scala}

\end{frame}
